\documentclass[11pt]{article}

% ======================
% Packages
% ======================
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{geometry}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{enumerate}

% ======================
% Page Layout
% ======================
\geometry{a4paper, margin=1in}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}

% ======================
% Colors & Code Styling
% ======================
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\small,
    breakatwhitespace=false,
    breaklines=true,
    captionpos=b,
    keepspaces=true,
    numbers=left,
    numbersep=5pt,
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    tabsize=2
}

\lstset{style=mystyle}

% ======================
% Theorem-like Environments
% ======================
\newtheorem{problem}{Problem}
\newtheorem{subproblem}{Subproblem}[problem]
\newtheorem{solution}{Solution}[problem]

% ======================
% Title Info
% ======================
\title{\textbf{Fundamental Algorithm Techniques} \\ Problem Set \#5} % \author{}
\date{\textcolor{red}{Review on March 02, 2026}} %Due: November 01, 2025}

% ======================
% Document
% ======================
\begin{document}

\maketitle



\begin{problem}[Graph and Tree Definitions, 5/10 pts]
Prove that the following definitions are all equivalent:
\begin{enumerate}
    \item A tree is a connected acyclic graph.
    \item A tree is one component of a forest. (A forest is an acyclic graph.)
    \item A tree is a connected graph with at most $V - 1$  edges.
    \item A tree is a minimally connected graph; removing any edge disconnects the graph.
    \item A tree is an acyclic graph with at least $V - 1$  edges.
    \item A tree is a maximally acyclic graph; adding an edge between any two vertices creates a cycle.
    \item A tree is a graph that contains a unique path between each pair of vertices.
\end{enumerate}

\end{problem}


\begin{problem}[Sparse representation of graphs, 5/10 pts]  
Given the following CSC (Compressed Sparse Column) representations for two graphs on vertices $\{A,B,C,D,E\}$ (indexed as $A\!\to\!0$, $B\!\to\!1$, $C\!\to\!2$, $D\!\to\!3$, $E\!\to\!4$):

\medskip

\noindent\textbf{Graph 1 (undirected):}  \\
\texttt{col\_pointers = [0, 2, 5, 8, 11, 12]}  \\
\texttt{row\_indices   = [1, 2, 0, 2, 3, 0, 1, 3, 1, 2, 4, 3]}  \\
\texttt{values        = [1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1]}

\medskip

\noindent\textbf{Graph 2 (directed):}  \\
\texttt{col\_pointers = [0, 0, 2, 4, 5, 7]} \\ 
\texttt{row\_indices   = [0, 3, 0, 1, 2, 1, 3]} \\ 
\texttt{values        = [1, 1, 1, 1, 1, 1, 1]}

\medskip

\noindent For each graph, reconstruct:  
(a) the adjacency matrix, and  
(b) a clear diagram of the graph (layout and style of your choice), (c) what is the unique cycle in directed graph (Describe it as e.g. X --> Y --> Z --> X).  
\end{problem}

\end{document}

%p.225 Algorithms Jeffe
